---
title: "Gun Control Chi Square"
author: "AnnaClaire Marley"
date: "11/14/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

I'm annaclaire and I'm adding some text here to see if my collaborators can get this file 

AC: Now Jill is also a collaborator 

Hi AC, this is Jill. I just wanted to add some text and say that this is awesome and wanted to know if you wanted to go to patagonia this weekend and use Ben's discount?

Creator (AnnaClaire)

Getting the gc_df.csv data, loading the tidyverse and gettng some summary counts

```{r}
library(tidyverse)
gc_df <- read_csv("gc_df.csv")

get_guns<- gc_df %>% 
  filter(gender != "NA", make_get_guns != "NA") %>% 
  count(gender, make_get_guns) %>% #set groupings for different categorical variables
  spread(make_get_guns, n) %>% 
  select(-gender)

rownames(get_guns) <- c("Female", "Male")
```


I'm the collaborator (Jill) and I am going to do Chi-square!
Does gender influence prefence on gun control?
Is there a significant difference in gun control perspectives (as related to access to guns) for males and females?
Is tehre a significant association between sex and gun control recommendations?
Is perception of gun control access independent of sex?

*All of these questions would lead us to think Chi-square is a good option.*

Chi-Square
```{r}

guns_prop <- prop.table(as.matrix(get_guns), 1) # instead of calculating proportions in entire table, only calculate proportions within rows
guns_prop

# Performing Chi-Square

guns_x2 <- chisq.test(get_guns)
guns_x2


```
Recommended government action on gun access differs significantly for males and females ($\chi^2$(`r guns_x2$parameter`) = ...., p < 0.001)
60% of women think it should be more difficult to get guns while only 40% of males think it should be more difficult to get guns. 



